EvoSuite at the SBST 2017 Tool Competition

### 2017-02-20 papers/sbst17/mainTable.tex
overall results

BCEL-1 &  14.0\% &  0.0\% &  18.0\% &  36.6\% &  17.2\% &  0.0\% &  0.0\% &  5.9\% &  0.0\% &  14.9\% &  18.6\% &  16.8\% &  0.0\% &  0.0\%\\ 

@@

BCEL-9 &  0.0\% &  0.0\% &  36.9\% &  0.0\% &  23.1\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  33.3\% &  0.0\% &  17.5\% &  0.0\% &  0.0\%\\ 

@@

FREEHEP-2 &  0.0\% &  0.0\% &  64.2\% &  95.4\% &  96.1\% &  96.8\% &  96.5\% &  0.0\% &  0.0\% &  4.0\% &  7.1\% &  7.4\% &  7.6\% &  7.1\%\\ 
FREEHEP-3 &  0.0\% &  0.0\% &  48.1\% &  74.8\% &  86.7\% &  81.7\% &  87.1\% &  0.0\% &  0.0\% &  11.1\% &  14.4\% &  16.2\% &  19.2\% &  21.5\%\\ 

@@

FREEHEP-6 &  0.0\% &  0.0\% &  86.4\% &  87.7\% &  88.3\% &  89.5\% &  89.5\% &  0.0\% &  0.0\% &  38.0\% &  46.7\% &  50.0\% &  41.3\% &  46.0\%\\ 

@@

FREEHEP-9 &  1.4\% &  1.4\% &  13.1\% &  22.5\% &  49.1\% &  29.7\% &  33.8\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  16.7\% &  15.8\% &  16.2\%\\ 
GSON-1 &  0.0\% &  0.0\% &  46.3\% &  68.5\% &  70.4\% &  70.4\% &  70.4\% &  0.0\% &  0.0\% &  45.4\% &  63.0\% &  65.7\% &  65.7\% &  63.9\%\\ 

@@

JXPATH-6 &  0.0\% &  0.0\% &  0.0\% &  48.6\% &  84.8\% &  83.3\% &  83.3\% &  0.0\% &  0.0\% &  0.0\% &  51.3\% &  82.7\% &  86.7\% &  78.7\%\\ 
JXPATH-7 &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 

@@

LA4J-3 &  0.0\% &  15.6\% &  0.0\% &  17.1\% &  38.9\% &  0.0\% &  20.3\% &  0.0\% &  10.8\% &  0.0\% &  10.5\% &  27.1\% &  0.0\% &  7.1\%\\ 
LA4J-4 &  0.0\% &  49.5\% &  71.7\% &  68.2\% &  71.7\% &  77.8\% &  80.8\% &  0.0\% &  33.1\% &  48.9\% &  52.3\% &  53.0\% &  43.9\% &  58.4\%\\ 
LA4J-5 &  0.0\% &  23.5\% &  32.6\% &  42.3\% &  54.4\% &  52.0\% &  44.4\% &  0.0\% &  14.9\% &  20.5\% &  24.1\% &  34.1\% &  20.3\% &  27.2\%\\ 

@@

LA4J-7 &  0.0\% &  7.5\% &  0.0\% &  21.7\% &  0.0\% &  0.0\% &  21.9\% &  0.0\% &  6.1\% &  0.0\% &  17.6\% &  0.0\% &  0.0\% &  17.1\%\\ 

@@

OKHTTP-5 &  0.0\% &  0.0\% &  3.6\% &  11.1\% &  23.8\% &  12.7\% &  33.3\% &  0.0\% &  0.0\% &  5.0\% &  12.0\% &  19.0\% &  11.8\% &  29.3\%\\ 

@@

OKHTTP-8 &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\% &  0.0\%\\ 

@@

RE2J-6 &  0.0\% &  0.0\% &  55.1\% &  56.7\% &  83.7\% &  84.3\% &  86.8\% &  0.0\% &  0.0\% &  42.0\% &  51.0\% &  69.2\% &  68.9\% &  66.3\%\\ 

>>>>

BCEL-1 & 14.0\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 18.0\% & 36.6\% & 17.2\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 5.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 14.9\% & 18.6\% & 16.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\ 

@@

BCEL-9 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 36.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 23.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 33.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\ 

@@

FREEHEP-2 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 64.2\% & 95.4\% & 96.1\% & 96.8\% & 96.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 4.0\% & 7.1\% & 7.4\% & 7.6\% & 7.1\%\\ 
FREEHEP-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 48.1\% & 74.8\% & 86.7\% & 81.7\% & 87.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 11.1\% & 14.4\% & 16.2\% & 19.2\% & 21.5\%\\ 

@@

FREEHEP-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 86.4\% & 87.7\% & 88.3\% & 89.5\% & 89.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 38.0\% & 46.7\% & 50.0\% & 41.3\% & 46.0\%\\ 

@@

FREEHEP-9 & 1.4\% & 1.4\% & 13.1\% & 22.5\% & 49.1\% & 29.7\% & 33.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 16.7\% & 15.8\% & 16.2\%\\ 
GSON-1 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 46.3\% & 68.5\% & 70.4\% & 70.4\% & 70.4\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 45.4\% & 63.0\% & 65.7\% & 65.7\% & 63.9\%\\ 

@@

JXPATH-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 48.6\% & 84.8\% & 83.3\% & 83.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 51.3\% & 82.7\% & 86.7\% & 78.7\%\\ 
JXPATH-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\ 

@@

LA4J-3 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 15.6\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.1\% & 38.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 20.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 10.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 10.5\% & 27.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 7.1\%\\ 
LA4J-4 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 49.5\% & 71.7\% & 68.2\% & 71.7\% & 77.8\% & 80.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 33.1\% & 48.9\% & 52.3\% & 53.0\% & 43.9\% & 58.4\%\\ 
LA4J-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 23.5\% & 32.6\% & 42.3\% & 54.4\% & 52.0\% & 44.4\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 14.9\% & 20.5\% & 24.1\% & 34.1\% & 20.3\% & 27.2\%\\ 

@@

LA4J-7 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 7.5\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 21.7\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 21.9\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 6.1\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.6\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 17.1\%\\ 

@@

OKHTTP-5 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 3.6\% & 11.1\% & 23.8\% & 12.7\% & 33.3\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 5.0\% & 12.0\% & 19.0\% & 11.8\% & 29.3\%\\ 

@@

OKHTTP-8 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\%\\ 

@@

RE2J-6 & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 55.1\% & 56.7\% & 83.7\% & 84.3\% & 86.8\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & \cellcolor{light-gray} \textcolor{black}{0.0}\% & 42.0\% & 51.0\% & 69.2\% & 68.9\% & 66.3\%\\ 

### 2017-02-20 papers/sbst17/paper_sbst17.tex
Acks
overall results

%\documentclass[times, 10pt,twocolumn]{article} 
%\usepackage{latex8}
%\usepackage{times}
\usepackage{amsfonts}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subfigure}
%\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,table]{xcolor}
%\usepackage{soul}
\usepackage{xspace}
\usepackage{boxedminipage}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{balance}

@@

%\documentstyle[times,art10,twocolumn,latex8]{article}

@@

\author{\IEEEauthorblockN{Authors}}

@@

The coverage results (line coverage and branch coverage) achieved by
\EVOSUITE on the benchmark classes are listed in
Table~\ref{table:coverage_results}. Coverage is generally in the
expected range, with clear increases for higher time budgets. Coverage
on several of the benchmarks from Closure is low, which matches
previous findings~\cite{shamshiri2015automatically}.

Results in terms of mutation scores and fault detection ratio (i.e.,
how many of the runs had at least one failing test on the
corresponding bug) are showing in
Table~\ref{table:fault_results}. Again the Closure results are
generally worse than those of other projects, both in terms of
mutation score and ratio of fault detection.

On average, \EVOSUITE generated 0.14 flaky tests per run, a value that
is significantly lower than that of any of the competing tools. This
is due to extensive efforts to isolate \EVOSUITE tests from the
execution environment~\cite{arcuri2014automated}. A few of these flaky
tests were introduced by recent changes to \EVOSUITE following
experiments on Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE
now includes assertions on the source of exceptions, similar to
commercial tools like Agitar One. %~\cite{agitarone}. 
Unfortunately, there were several instances in the competition where these assertions
lead to flaky tests. For example, the following is an excerpt from a
test for the Defects4J bug Lang-41, generated by \EVOSUITE:
\vspace{1em}

\begin{lstlisting}
@Test(timeout = 4000)
public void test19()  throws Throwable  {
 Class<Double> class0 = Double.class;
 String string0 = ClassUtils.getPackageName(class0);
 try { 
   ClassUtils.getClass(string0);
   fail("Expecting exception: ClassNotFoundException"); 
 } catch(ClassNotFoundException e) {
   assertThrownBy("java.net.URLClassLoader", e);
 }
}
\end{lstlisting}

While compiling and executing this test with JUnit works without
problems, the mutation analysis step of the competition used Ant to
run the tests; Ant uses a complex setup of classloaders that
eventually leads to the \texttt{assertThrownBy} in the above example
to fail, as the source of the exception is a different one.

There are 15 runs in total where \EVOSUITE did not produce any test
suites; these are only for higher time budgets (240s, 480s). The
majority of these runs are due to \EVOSUITE not terminating before the
hard timeout of the competition infrastructure. This may happen, for
example, when test execution on the class under test takes long (e.g.,
timeouts), and when resetting the static state of the classes under
test takes a long time. However, this number is still lower than the
number of erroneous runs compared to other tools, and in the remaining
1617 runs of the competition \EVOSUITE terminated in time and produced
at least two tests. In 13 of these, \EVOSUITE produced a test suite
with a compilation error.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by 
%the EPSRC project ``EXOGEN'' (EP/K030353/1), a Google Focused Research Award on ``Test
%Amplification'', and by 
the National Research Fund, Luxembourg (FNR/P10/03).

>>>>

%\documentclass[times, 10pt,twocolumn]{article} 
%\usepackage{latex8}
%\usepackage{times}
\usepackage{amsfonts}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{float}
\usepackage[numbers,sort&compress,square]{natbib}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subfigure}
%\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{soul}
\usepackage{xspace}
\usepackage{boxedminipage}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{balance}
\definecolor{light-gray}{gray}{0.90}

@@

\input{macros}

@@

\author{\IEEEauthorblockN{Gordon Fraser\IEEEauthorrefmark{1}, Jos\'e
    Miguel Rojas\IEEEauthorrefmark{2}, Jos\'e Campos\IEEEauthorrefmark{3}}
  \IEEEauthorblockA{The University of Sheffield\\Sheffield, United Kingdom\\
    \{\IEEEauthorrefmark{1}gordon.fraser,
    \IEEEauthorrefmark{2}j.rojas, \IEEEauthorrefmark{3}jose.campos\}@sheffield.ac.uk} 
\and
\IEEEauthorblockN{Andrea Arcuri}
  \IEEEauthorblockA{Westerdals Oslo ACT, Norway\\and University of Luxembourg, Luxembourg\\arcand@westerdals.no}
}

@@

% overall results
Table~\ref{table:results} lists the branch coverage and mutation
analysis results achieved by \EVOSUITE on all benchmark classes in the
contest. Coverage is generally in the expected range, with clear
increases for higher time budgets as expected, except for
$budget=300s$, where a decrease is observed, possibly due to crashes
or \emph{out-of-memory} errors\TODO{confirm this conjecture}. With
$budget=480s$, the average branch coverage achieved was \AvgCovG
(slightly higher than last year's $65.6\%$) and the average mutation
score was \AvgMutG (considerably higher than last year's $41.0\%$).

% Coverage on several
% of the benchmarks from Closure is low, which matches previous
% findings~\cite{shamshiri2015automatically}.

% Results in terms of mutation scores and fault detection ratio (i.e.,
% how many of the runs had at least one failing test on the
% corresponding bug) are showing in
% Table~\ref{table:fault_results}. Again the Closure results are
% generally worse than those of other projects, both in terms of
% mutation score and ratio of fault detection.

\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
tools (\FlakyTthree by T3, \FlakyJtexpert by JTExpert, and
\FlakyRandoop by Randoop). We attribute these results---also
consistent with previous years' results---to the way \EVOSUITE handles
execution environments during test generation (e.g., controlling the
static state of the class under test, mocking interactions with the
file system, system calls like \texttt{System.in} and
\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.

% A few of these flaky tests were introduced by recent changes to
% \EVOSUITE following experiments on
% Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE now includes
% assertions on the source of exceptions, similar to commercial tools
% like Agitar One. %~\cite{agitarone}.
% Unfortunately, there were several instances in the competition where
% these assertions lead to flaky tests. For example, the following is an
% excerpt from a test for the Defects4J bug Lang-41, generated by
% \EVOSUITE: \vspace{1em}

% \begin{lstlisting}
% @Test(timeout = 4000)
% public void test19()  throws Throwable  {
%  Class<Double> class0 = Double.class;
%  String string0 = ClassUtils.getPackageName(class0);
%  try { 
%    ClassUtils.getClass(string0);
%    fail("Expecting exception: ClassNotFoundException"); 
%  } catch(ClassNotFoundException e) {
%    assertThrownBy("java.net.URLClassLoader", e);
%  }
% }
% \end{lstlisting}

% While compiling and executing this test with JUnit works without
% problems, the mutation analysis step of the competition used Ant to
% run the tests; Ant uses a complex setup of classloaders that
% eventually leads to the \texttt{assertThrownBy} in the above example
% to fail, as the source of the exception is a different one.

% There are 15 runs in total where \EVOSUITE did not produce any test
% suites; these are only for higher time budgets (240s, 480s). The
% majority of these runs are due to \EVOSUITE not terminating before the
% hard timeout of the competition infrastructure. This may happen, for
% example, when test execution on the class under test takes long (e.g.,
% timeouts), and when resetting the static state of the classes under
% test takes a long time. However, this number is still lower than the
% number of erroneous runs compared to other tools, and in the remaining
% 1617 runs of the competition \EVOSUITE terminated in time and produced
% at least two tests. In 13 of these, \EVOSUITE produced a test suite
% with a compilation error.

@@

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by the EPSRC
project ``GREATEST'' (EP/N023978/1), and by the National Research
Fund, Luxembourg (FNR/P10/03).
